Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-27 ms.tex
cutting fat - and lots of it8

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate $\dot{M}/\dot{M}_{\rm edd}$ as a
  function of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$, solid).
  Black lines show the accretion rate calculated from equation
  (\ref{eq:eddr_analytic}) using our estimate of the gas heating rate
  provided at $z = 0$ by the average star formation histories for each
  galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the maximum
  accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).  Red
  lines show the accretion rate obtained if Compton heating alone was
  acting (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum
  accretion rate for a thermally stable flow near the stagnation
  radius (eq.~[\ref{eq:Mdotmax}]).  We also show Eddington ratios
  inferred for SgrA* from \citet{Quataert:2004a} (gray circles), for
  NGC3115 from \citet{ShcherbakovWong+:2014a} (gray diamonds), and for
  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (gray
  triangles). Note that the actual black hole accretion rate could one
  to several orders of magnitude smaller due to the presence of small
  scale outflows. Thus the plot is really showing
  the gas inflow rate on large scales (e.g. near the stagnation
  radius) {\it Bottom panel:} Growth times $\Mbh/\dot{M}_{\bullet}$ in units of
  the Hubble time $\th$ for each of the accretion rates shown in the
  top panel, where $\dot{M}_{\bullet} = 0.1\dot{M}$ to account for the fraction of the inflowing matter lost to outflows from the accretion disk.}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency calculated by \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of the mass inflowing on large scales that reaches the SMBH.  Shown
  for comparison are the X-ray luminosities calculated for the maximum
  thermally-stable accretion rate ({\it dashed orange line};
  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
  heating-regulated accretion rate ({\it dashed pink line};
  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
  corresponding to each SMBH mass.}
\end{figure*}

If the nuclei of elliptical galaxies are heated as expected for the
average SFH of galaxies with similar mass, then to first order we
predict that $\langle L_{X}/L_{\rm edd}\rangle$ should be a weakly
increasing function of BH mass.  This result is in tension with the
observed down-sizing trend that the average Eddington ratio is seen to
decrease (albeit weakly) with $M_{\bullet}$, especially in the
$\epsilon_X= (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$ model.
However, one must keep in mind the enormous uncertainty in calculating
the luminosity of the accretion flow close to the black hole in a
single waveband based on the feeding rate on larger scales.  If disk
outflows carry away most of the infalling mass before it reaches X-ray
producing radii (e.g.~\citealt{Blandford&Begelman99};
\citealt{Li+13}), then the angular momentum of the infalling gas might
also influence the X-ray luminosity, in a way that could depend
systematically on the stellar population and hence $M_{\bullet}$.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate $\dot{M}/\dot{M}_{\rm edd}$ as a
  function of black hole mass $M_{\bullet}$, shown for core
  ($\Gamma=0.1$, dot-dashed) and cusp galaxies ($\Gamma=0.8$, solid).
  Black lines show the accretion rate calculated from equation
  (\ref{eq:eddr_analytic}) using the heating rate provided at $z = 0$ by the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the maximum accretion set by Ia supernovae blow-out, $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$ (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum
  accretion rate for a thermally stable flow near the stagnation radius, $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).  Also shown are the inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray circles), for
  NGC3115 from \citet{ShcherbakovWong+:2014a} (gray diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a} (gray
  triangles).  {\it Bottom panel:} Growth times $t_{\rm grow} \equiv \Mbh/\dot{M}_{\bullet}$ in units of
  the Hubble time $\th$ for each of the accretion rates shown in the
  top panel, where $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to account for the fraction of inflowing mass lost to disk outflows on small scales.}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})=0.3 \Mbheight^{-0.24}$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= \alpha \epsilon_{\rm bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the radiative efficiency of low luminosity accretion disks calculated by \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$ is the fraction of the mass inflowing on large scales that reaches the SMBH.  Shown
  for comparison are the X-ray luminosities calculated for the maximum
  thermally-stable accretion rate ({\it dashed orange line};
  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
  heating-regulated accretion rate ({\it dashed pink line};
  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
  corresponding to each SMBH mass.}
\end{figure*}

If the nuclei of elliptical galaxies are heated as expected for the
average SFH of galaxies with similar mass, then to first order we
predict that $\langle L_{X}/L_{\rm edd}\rangle$ should be a weakly
increasing function of BH mass.  This result is in tension with the
observed down-sizing trend that the average Eddington ratio is seen to
decrease (albeit weakly) with $M_{\bullet}$, especially in the model where
$\epsilon_X$ increases with the Eddington ratio.
However, one must keep in mind the enormous uncertainty in calculating
the luminosity of the accretion flow close to the black hole in a
single waveband based on the feeding rate on larger scales.  If disk
outflows carry away most of the infalling mass before it reaches X-ray
producing radii (e.g.~\citealt{Blandford&Begelman99};
\citealt{Li+13}), then the angular momentum of the infalling gas might
also influence the X-ray luminosity, in a way that could depend
systematically on the stellar population and hence $M_{\bullet}$.
